Issues with Dynamical Measurements Across the Disk

### 2019-02-15 paper/ms.tex
Small changes

\subsection{Quantification of the effect of systematic coordinate-system
errors} \label{ssec:quant}
First, we illustrate the phase-dependence of an
example systematic error in the Galactocentric coordinate system. We will
consider three orbits in the model potential described in \S
\ref{ssec:action_comp} that are typical of stars in the stellar thin disk,
stellar thick disk, and the stellar halo. We summarize their initial positions
in phase space and the actions computed by integrating their orbits in the
correct potential in Table~\ref{tab:orbits}. Each orbit, integrated without
systematic coordinate errors, is plotted in Appendix~\ref{app:orbits}. We will
refer to these orbits by their names (thin-disk, thick-disk, halo) henceforth.

@@

One could then make a further selection by requiring that the action of each
field star $i$ be close to the cluster's actions to within some bound, i.e.
$\bm{J}_i - \bm{J}_c \in V_e$ where $V_e$ is some volume in action space
enclosing a region of acceptable error. A natural choice for $V_e$ is to
center it at the origin and allow its extent to be the intrinsic action-space
dispersion of a disrupted cluster. This dispersion can be estimated as
\citep[\S~8.3.3][]{2008gady.book.....B}
\beq \label{eq:action_disp}
\frac{\Delta J_i}{J_i} \sim \left(\frac{m_c}{M}\right)^{1/3}\text{,}
\eeq
where $m_c$ is the mass of the cluster and $M$ is the mass enclosed by the
cluster's orbit. A more sophisticated treatment of the action-space dispersion
of disrupted clusters can be obtained by following
\citet{2011MNRAS.413.1852E}, but such a treatment is premature for this work.

>>>>

\subsection{Quantification of the effect of systematic coordinate-system
errors} \label{ssec:quant} First, we illustrate the phase-dependence of an
example systematic error in the Galactocentric coordinate system. We will
consider three orbits in the model potential described in
Section~\ref{ssec:action_comp} that are typical of stars in the stellar thin
disk, stellar thick disk, and the stellar halo. We summarize their initial
positions in phase space and the actions computed by integrating their orbits
in the correct potential in Table~\ref{tab:orbits}. Each orbit, integrated
without systematic coordinate errors, is plotted in Appendix~\ref{app:orbits}.
We will refer to these orbits by their names (thin-disk, thick-disk, halo)
henceforth.

@@

One could then make a further selection by requiring that the action of each
field star $i$ be close to the cluster's actions to within some bound, i.e.
$\bm{J}_i - \bm{J}_c \in V_e$ where $V_e$ is some volume in action space
enclosing a region of acceptable error. A natural choice for $V_e$ is to
center it at the origin and allow its extent to be the intrinsic action-space
dispersion of a disrupted cluster. This dispersion can be estimated as
\citep[Section~8.3.3][]{2008gady.book.....B}
\beq \label{eq:action_disp}
\frac{\Delta J_i}{J_i} \sim \left(\frac{m_c}{M}\right)^{1/3}\text{,}
\eeq
where $m_c$ is the mass of the cluster and $M$ is the mass enclosed by the
cluster's orbit. A more sophisticated treatment of the action-space dispersion
of disrupted clusters can be obtained by following
\citet{2011MNRAS.413.1852E}, but such a treatment is premature for this work.
